---
title: "CCHS Documentation Catalog"
subtitle: "Canadian Community Health Survey (2001-2023)"
---

```{r setup}
library(yaml)
library(dplyr)
library(DT)

# Load catalog
catalog <- yaml::read_yaml("data/catalog/cchs_catalog.yaml")
files <- catalog$files
```

## Browse files

Use the search box and column filters to find specific documents. Click any link to download the file directly.

```{r catalog-table}
# Convert to data frame
df <- data.frame(
  Year = sapply(files, function(x) x$year),
  Category = sapply(files, function(x) x$category),
  Type = sapply(files, function(x) x$doc_type),
  Language = sapply(files, function(x) x$language),
  Filename = sapply(files, function(x) x$filename),
  URL = sapply(files, function(x) x$github_url),
  stringsAsFactors = FALSE
)

# Create clickable links
df$Download <- paste0('<a href="', df$URL, '" target="_blank">Download</a>')

# Format category names
df$Category <- gsub("-", " ", df$Category)
df$Category <- tools::toTitleCase(df$Category)

# Format type
df$Type <- tools::toTitleCase(df$Type)

# Format language
df$Language <- ifelse(df$Language == "EN", "English", "French")

# Select display columns
display_df <- df[, c("Year", "Category", "Type", "Language", "Filename", "Download")]

datatable(
  display_df,
  escape = FALSE,  # Allow HTML in Download column
  filter = "top",
  options = list(
    pageLength = 25,
    scrollX = TRUE,
    columnDefs = list(
      list(width = "60px", targets = 0),   # Year
      list(width = "120px", targets = 1),  # Category
      list(width = "80px", targets = 2),   # Type
      list(width = "80px", targets = 3),   # Language
      list(width = "80px", targets = 5)    # Download
    )
  ),
  rownames = FALSE
)
```

## Summary statistics

### By year

```{r by-year}
year_counts <- table(df$Year)
knitr::kable(
  data.frame(
    Year = names(year_counts),
    Files = as.numeric(year_counts)
  ),
  col.names = c("Year", "Files"),
  align = c("l", "r")
)
```

### By category

```{r by-category}
cat_counts <- sort(table(df$Category), decreasing = TRUE)
knitr::kable(
  data.frame(
    Category = names(cat_counts),
    Files = as.numeric(cat_counts)
  ),
  col.names = c("Category", "Files"),
  align = c("l", "r")
)
```

## Data sources

Files in this catalog come from:

- **OSF.io** - Master and Share files from the [CCHS Docs project](https://osf.io/6p3n9/)
- **Google Drive** - Legacy PUMF documentation
- **Borealis/ODESSI** - DDI XML metadata (extracted to YAML)

See [data sources](https://github.com/Big-Life-Lab/cchsflow-docs#data-sources) for details.
