---
title: "CHMS Documentation Catalog"
subtitle: "Canadian Health Measures Survey (Cycles 1-6)"
---

```{r setup}
library(yaml)
library(dplyr)
library(DT)

# Load catalog
catalog <- yaml::read_yaml("data/catalog/chms_catalog.yaml")
files <- catalog$files
```

## Browse files

Use the search box and column filters to find specific documents. Click any link to download the file directly.

```{r catalog-table}
# Convert to data frame
df <- data.frame(
  Cycle = sapply(files, function(x) gsub("cycle", "Cycle ", x$chms_cycle)),
  Component = sapply(files, function(x) x$chms_component),
  Category = sapply(files, function(x) x$category),
  Language = sapply(files, function(x) x$language),
  Filename = sapply(files, function(x) x$filename_original),
  URL = sapply(files, function(x) x$github_url),
  stringsAsFactors = FALSE
)

# Create clickable links
df$Download <- paste0('<a href="', df$URL, '" target="_blank">Download</a>')

# Format category names
df$Category <- gsub("-", " ", df$Category)
df$Category <- tools::toTitleCase(df$Category)

# Format component names
component_names <- c(
  "gen" = "General",
  "hhd" = "Household",
  "clc" = "Clinic",
  "ams" = "Activity Monitor",
  "fast" = "Fasting",
  "nel" = "Environmental",
  "med" = "Medication",
  "inc" = "Income",
  "hcl" = "Health Clinic"
)
df$Component <- ifelse(df$Component %in% names(component_names),
                       component_names[df$Component],
                       df$Component)

# Format language
df$Language <- ifelse(df$Language == "e", "English", "French")

# Select display columns
display_df <- df[, c("Cycle", "Component", "Category", "Language", "Filename", "Download")]

datatable(
  display_df,
  escape = FALSE,
  filter = "top",
  options = list(
    pageLength = 25,
    scrollX = TRUE
  ),
  rownames = FALSE
)
```

## Summary

### By cycle

```{r by-cycle}
cycle_counts <- table(df$Cycle)
knitr::kable(
  data.frame(
    Cycle = names(cycle_counts),
    Files = as.numeric(cycle_counts)
  ),
  col.names = c("Cycle", "Files"),
  align = c("l", "r")
)
```

### By component

```{r by-component}
comp_counts <- sort(table(df$Component), decreasing = TRUE)
knitr::kable(
  data.frame(
    Component = names(comp_counts),
    Files = as.numeric(comp_counts)
  ),
  col.names = c("Component", "Files"),
  align = c("l", "r")
)
```

## About CHMS

The Canadian Health Measures Survey (CHMS) collects health data through:

- **Household interviews** - Demographics, health status, lifestyle
- **Clinic visits** - Physical measurements, blood/urine samples
- **Activity monitoring** - Accelerometer data for physical activity

Data is organised by **cycle** (collection period) and **component** (measurement type).

**Source**: Files mirrored from [OSF.io CHMS Docs](https://osf.io/buva4/)
