---
title: "Canadian Health Survey Documentation"
subtitle: "CCHS & CHMS Documentation Catalog"
---

```{r setup}
library(yaml)
library(dplyr)

# Load catalogs
cchs <- yaml::read_yaml("data/catalog/cchs_catalog.yaml")
chms <- yaml::read_yaml("data/catalog/chms_catalog.yaml")
```

## Overview

This site provides searchable access to documentation for two major Canadian health surveys:

- **Canadian Community Health Survey (CCHS)**: `r length(cchs$files)` files (2001-2023)
- **Canadian Health Measures Survey (CHMS)**: `r length(chms$files)` files (Cycles 1-6)

## Quick links

| Survey | Catalog | Core documents |
|--------|---------|----------------|
| CCHS | [Browse all files](cchs-catalog.qmd) | [Questionnaires](cchs-catalog.qmd#category=questionnaire), [Data dictionaries](cchs-catalog.qmd#category=data-dictionary), [User guides](cchs-catalog.qmd#category=user-guide) |
| CHMS | [Browse all files](chms-catalog.qmd) | [User guides](chms-catalog.qmd#category=user-guide), [Questionnaires](chms-catalog.qmd#category=questionnaire) |

## Downloads

For bulk downloads, see:

- [GitHub Releases](https://github.com/Big-Life-Lab/cchsflow-docs/releases) - Curated collections (ZIP files)
- [Downloads page](downloads.qmd) - Instructions for creating custom collections

## Coverage summary

### CCHS

```{r cchs-summary}
cchs_files <- cchs$files

# By doc type
doc_types <- table(sapply(cchs_files, function(x) x$doc_type))
langs <- table(sapply(cchs_files, function(x) x$language))

knitr::kable(
  data.frame(
    Type = names(doc_types),
    Files = as.numeric(doc_types)
  ),
  col.names = c("Document Type", "Files"),
  align = c("l", "r")
)
```

### CHMS

```{r chms-summary}
chms_files <- chms$files

cycles <- table(sapply(chms_files, function(x) x$chms_cycle))

knitr::kable(
  data.frame(
    Cycle = gsub("cycle", "Cycle ", names(cycles)),
    Files = as.numeric(cycles)
  ),
  col.names = c("Cycle", "Files"),
  align = c("l", "r")
)
```

## Related resources

- [CCHS NotebookLM](https://notebooklm.google.com/notebook/d89f1bf8-1eb5-4bc7-bfd4-462be2c01a08) - AI assistant for exploring CCHS documentation
- [cchsflow](https://github.com/Big-Life-Lab/cchsflow) - R package for harmonising CCHS variables
- [cchsflow-data](https://github.com/Big-Life-Lab/cchsflow-data) - CCHS PUMF data files
