---
title: "CCHS OSF.io Sync Workflow"
subtitle: "Automated Pipeline for Synchronization and Change Detection"
author: "CCHS Documentation System"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    theme: cosmo
    code-fold: false
    code-summary: "Show R Code"
execute:
  echo: true
  warning: false
  message: false
---

# Overview

This document serves as both a **workflow guide** and an **executable pipeline** for managing CCHS OSF.io synchronization using our git-based versioning system.

## Key Features

- **Git-based versioning** for metadata tracking
- **Automated change detection** comparing local vs OSF.io
- **Parameterized report generation** from templates
- **Complete workflow automation** with error handling

```{r setup}
#| include: false
library(here)
library(git2r)

# Load our sync systems
source(here("R/osf_sync_system.R"))
source(here("R/osf_versioning_system.R"))
```

# Workflow Steps

## 1. Initialize Git Versioning

Set up git tracking for metadata files while ignoring large data files:

```{r init-versioning}
#| eval: false

# Initialize git repository for metadata tracking
repo <- init_osf_versioning()

# This creates:
# - Git repo in cchs-osf-docs/
# - .gitignore for data files (keeps metadata)
# - Initial commit with current metadata
```

## 2. Create Baseline Snapshot

Capture current OSF.io state as baseline for future comparisons:

```{r create-baseline}
#| eval: false

# Update all metadata and create baseline commit
baseline_sha <- create_baseline_commit()

# This:
# - Updates metadata for all years (2001-2023)
# - Stages all metadata changes
# - Creates git commit with timestamp
# - Returns commit SHA for reference
```

## 3. Automated Change Detection

Compare current OSF.io state with previous commits to detect changes:

```{r detect-changes}
#| eval: false

# Git-based change detection
changes <- detect_changes_with_git(base_commit = "HEAD~1")

# This compares:
# - Current OSF.io metadata vs last commit
# - Returns detailed change analysis
# - Identifies added/removed/modified files by year
```

## 4. Automated Sync Validation

Complete validation workflow with automatic file downloads:

```{r sync-validation}
#| eval: false

# Complete sync validation and update
changes <- automated_sync_validation(
  auto_download = TRUE,    # Download missing files
  commit_changes = TRUE    # Commit new files to git
)

# This:
# - Detects all changes across years
# - Downloads missing/updated files
# - Updates local metadata
# - Commits changes to git
```

## 5. Generate Updated Reports

Create standardized reports from current sync status:

```{r generate-report}
#| eval: false

# Generate parameterized QMD report
report_file <- generate_sync_report()

# This creates:
# - Timestamped QMD report in reports/
# - GT tables with sync status
# - Detailed change breakdowns
# - Actionable recommendations
```

# Complete Workflow Execution

## One-Command Pipeline

Execute the entire workflow with a single function:

```{r complete-workflow}
#| eval: false

# End-to-end workflow
results <- run_complete_workflow()

# Returns:
# - Detailed change analysis
# - Generated report filename
# - Summary statistics
```

## Manual Step-by-Step

For more control, run each step individually:

```{r manual-workflow}
#| eval: false

# Step 1: Initialize
repo <- init_osf_versioning()

# Step 2: Create baseline
baseline_sha <- create_baseline_commit("Weekly sync baseline - manual")

# Step 3: Detect changes
changes <- detect_changes_with_git()

# Step 4: Download updates if needed
if(any(sapply(changes, function(x) x$has_changes))) {
  cat("Changes detected, updating files...\n")
  for(year_str in names(changes)) {
    year <- as.numeric(year_str)
    if(changes[[year_str]]$has_changes) {
      download_year_files(year, force = TRUE)
    }
  }
}

# Step 5: Generate report
report_file <- generate_sync_report(changes)

cat(sprintf("Workflow complete. Report: %s\n", report_file))
```

# Scheduling and Automation

## Recommended Schedule

- **Daily**: Quick change detection (no downloads)
- **Weekly**: Full sync validation with downloads
- **Monthly**: Complete workflow with detailed reporting

## Cron Job Example

```bash
# Daily change detection (8 AM)
0 8 * * * cd /path/to/cchsflow-docs && Rscript -e "source('R/osf_versioning_system.R'); detect_changes_with_git()"

# Weekly full sync (Sunday 6 AM)  
0 6 * * 0 cd /path/to/cchsflow-docs && Rscript -e "source('R/osf_versioning_system.R'); run_complete_workflow()"
```

## GitHub Actions Integration

```yaml
name: OSF Sync Check
on:
  schedule:
    - cron: '0 6 * * 1'  # Monday 6 AM
  workflow_dispatch:

jobs:
  sync-check:
    runs-on: ubuntu-latest
    steps:
      - uses: actions/checkout@v3
      - uses: r-lib/actions/setup-r@v2
      - name: Install dependencies
        run: Rscript -e "install.packages(c('httr', 'jsonlite', 'yaml', 'git2r', 'gt'))"
      - name: Run sync workflow
        run: Rscript -e "source('R/osf_versioning_system.R'); run_complete_workflow()"
        env:
          OSF_PAT: ${{ secrets.OSF_PAT }}
```

# Troubleshooting

## Common Issues

1. **Git not initialized**: Run `init_osf_versioning(force_init = TRUE)`
2. **OSF authentication**: Check `OSF_PAT` environment variable
3. **Large file issues**: Ensure `.gitignore` is properly configured
4. **Merge conflicts**: Review metadata changes manually

## System Status Check

```{r status-check}
#| eval: false

# Quick system health check
cat("=== SYSTEM STATUS CHECK ===\n")

# Check git repository
repo_path <- here("cchs-osf-docs")
if(dir.exists(file.path(repo_path, ".git"))) {
  cat("✅ Git repository: Active\n")
} else {
  cat("❌ Git repository: Not initialized\n")
}

# Check OSF authentication
tryCatch({
  test_osf_authentication()
  cat("✅ OSF authentication: Working\n")
}, error = function(e) {
  cat("❌ OSF authentication: Failed\n")
})

# Check metadata files
metadata_files <- list.files(file.path(repo_path, "osf-metadata"), pattern = "*.yaml")
cat(sprintf("📄 Metadata files: %d found\n", length(metadata_files)))

cat("=== STATUS CHECK COMPLETE ===\n")
```

# Integration with Existing System

## Compatibility

This versioning system integrates seamlessly with:

- **Existing OSF sync functions** (`osf_sync_system.R`)
- **Current metadata structure** (YAML files)
- **Manual QMD reports** (backward compatible)
- **UID system** (no conflicts)

## Migration Path

1. **Keep existing workflows** - No breaking changes
2. **Add git tracking** - Versioning is additive
3. **Gradually adopt automation** - Can run manual/auto side-by-side
4. **Replace manual reports** - When comfortable with automation

---

**Workflow Ready**: This system provides complete automation while maintaining flexibility for manual operations.

**Next Steps**: Execute `run_complete_workflow()` to begin automated OSF.io management.