---
title: "CCHS Documentation Catalog"
subtitle: "Canadian Community Health Survey File Inventory"
author: "CCHS Documentation Project"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-depth: 3
    theme: bootstrap
    code-fold: true
    embed-resources: true
  pdf:
    toc: true
    toc-depth: 2
    papersize: letter
    geometry:
      - top=1in
      - left=1in
      - right=1in
      - bottom=1in
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(dplyr)
library(gt)
library(DT)
library(ggplot2)
library(htmltools)

# Load CCHS structure and categorization functions
source("R/load_cchs_structure.R")
source("R/cchs_file_download.R")

# Load data
load_cchs_structure()
categorized_files <- categorize_all_files()
```

# Executive Summary

The Canadian Community Health Survey (CCHS) documentation spans **`r length(get_expected_years())` survey years** from 2001 to 2023, covering both early biannual cycles and modern annual surveys.

```{r summary-stats}
# Calculate summary statistics
total_files <- sum(sapply(categorized_files, length))
years_with_files <- length(categorized_files)
english_files <- length(filter_files(categorized_files, languages = "english"))

# File type counts
all_files_flat <- unlist(categorized_files, recursive = FALSE)
type_counts <- table(sapply(all_files_flat, function(x) x$file_type))
lang_counts <- table(sapply(all_files_flat, function(x) x$language))
```

**Current Inventory:**

- **Total Files**: `r total_files` files across `r years_with_files` survey years
- **English Files**: `r english_files` files
- **File Types**: `r length(type_counts)` different document types
- **Survey Coverage**: `r min(get_expected_years())` - `r max(get_expected_years())`

# Survey Overview

## CCHS Survey Evolution

The CCHS methodology evolved from biannual cycles to annual data collection:

- **Early Cycles (2001-2005)**: Biannual surveys with cycle naming (1.1, 2.1, 3.1)
- **Annual Surveys (2006-2023)**: Yearly data collection with standardized structure

```{r survey-overview-table}
# Create survey overview table
expected_years <- get_expected_years()
overview_data <- data.frame(
  Year = expected_years,
  Survey_Type = ifelse(expected_years %in% c(2001, 2003, 2005), "Cycle", "Annual"),
  Cycle_Name = case_when(
    expected_years == 2001 ~ "1.1",
    expected_years == 2003 ~ "2.1", 
    expected_years == 2005 ~ "3.1",
    TRUE ~ "12-Month"
  ),
  Folder_Status = ifelse(as.character(expected_years) %in% names(categorized_files), "✓ Created", "Missing"),
  File_Count = sapply(expected_years, function(y) {
    if (as.character(y) %in% names(categorized_files)) {
      length(categorized_files[[as.character(y)]])
    } else {
      0
    }
  })
)

overview_data %>%
  gt() %>%
  tab_header(
    title = "CCHS Survey Years and Documentation Status"
  ) %>%
  cols_label(
    Year = "Year",
    Survey_Type = "Survey Type", 
    Cycle_Name = "Cycle/Period",
    Folder_Status = "Folder Status",
    File_Count = "Files Found"
  ) %>%
  cols_align(
    align = "center",
    columns = c(Year, File_Count)
  ) %>%
  tab_style(
    style = cell_fill(color = "lightgreen", alpha = 0.3),
    locations = cells_body(
      columns = Folder_Status,
      rows = Folder_Status == "✓ Created"
    )
  ) %>%
  tab_style(
    style = cell_fill(color = "lightcoral", alpha = 0.3),
    locations = cells_body(
      columns = Folder_Status, 
      rows = Folder_Status == "Missing"
    )
  )
```

# Document Type Analysis

## File Type Distribution

```{r file-type-chart}
# Create file type visualization
type_df <- data.frame(
  File_Type = names(type_counts),
  Count = as.numeric(type_counts)
) %>%
  arrange(desc(Count))

ggplot(type_df, aes(x = reorder(File_Type, Count), y = Count)) +
  geom_col(fill = "steelblue", alpha = 0.7) +
  coord_flip() +
  labs(title = "Distribution of File Types",
       x = "Document Type",
       y = "Number of Files") +
  theme_minimal()
```

```{r file-type-table}
type_df %>%
  gt() %>%
  tab_header(
    title = "File Types Available"
  ) %>%
  cols_label(
    File_Type = "Document Type",
    Count = "File Count"
  ) %>%
  cols_align(
    align = "center",
    columns = Count
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = File_Type
    )
  )
```

## Document Availability Matrix

```{r availability-matrix}
# Create availability matrix for key document types
key_types <- c("data_dictionary", "questionnaire", "user_guide", "derived_variables", "cv_tables")

# Get years that have files
years_with_data <- names(categorized_files)

# Create matrix
availability_matrix <- matrix(FALSE, 
                             nrow = length(years_with_data), 
                             ncol = length(key_types),
                             dimnames = list(years_with_data, key_types))

for (year in years_with_data) {
  year_files <- categorized_files[[year]]
  year_types <- sapply(year_files, function(x) x$file_type)
  
  for (type in key_types) {
    if (type %in% year_types) {
      availability_matrix[year, type] <- TRUE
    }
  }
}

# Convert to data frame for display
availability_df <- as.data.frame(availability_matrix)
availability_df$Year <- rownames(availability_df)
availability_df <- availability_df[, c("Year", key_types)]

# Convert TRUE/FALSE to checkmarks/X
display_matrix <- availability_df
for (col in key_types) {
  display_matrix[[col]] <- ifelse(display_matrix[[col]], "✓", "✗")
}

display_matrix %>%
  gt() %>%
  tab_header(
    title = "Document Availability by Year"
  ) %>%
  cols_label(
    Year = "Year",
    data_dictionary = "Data Dictionary",
    questionnaire = "Questionnaire", 
    user_guide = "User Guide",
    derived_variables = "Derived Variables",
    cv_tables = "CV Tables"
  ) %>%
  cols_align(
    align = "center",
    columns = c(data_dictionary, questionnaire, user_guide, derived_variables, cv_tables)
  ) %>%
  tab_style(
    style = cell_fill(color = "lightgreen", alpha = 0.3),
    locations = cells_body(
      columns = everything(),
      rows = data_dictionary == "✓" | questionnaire == "✓" | user_guide == "✓" | derived_variables == "✓" | cv_tables == "✓"
    )
  )
```

# Detailed File Inventory

## English Language Documents

```{r english-files-table}
# Get all English files with details
english_files_list <- filter_files(categorized_files, languages = "english")

if (length(english_files_list) > 0) {
  english_df <- data.frame(
    Year = sapply(english_files_list, function(x) x$survey_year),
    File_Type = sapply(english_files_list, function(x) x$file_type),
    Filename = sapply(english_files_list, function(x) x$filename),
    Path = sapply(english_files_list, function(x) x$path),
    stringsAsFactors = FALSE
  ) %>%
    arrange(Year, File_Type, Filename)
  
  datatable(english_df, 
            caption = "Complete English File Inventory",
            options = list(pageLength = 15, scrollX = TRUE),
            filter = 'top')
} else {
  cat("No English language files found.")
}
```

## Files by Survey Year

```{r year-table-function}
# Function to create GT table for a specific year
create_year_table <- function(year) {
  if (year %in% names(categorized_files)) {
    year_files <- categorized_files[[year]]
    
    if (length(year_files) > 0) {
      year_df <- data.frame(
        Filename = sapply(year_files, function(x) x$filename),
        Type = sapply(year_files, function(x) x$file_type),
        Language = sapply(year_files, function(x) x$language),
        Extension = sapply(year_files, function(x) x$extension),
        Path = sapply(year_files, function(x) x$path),
        stringsAsFactors = FALSE
      )
      
      year_df %>%
        gt() %>%
        tab_header(
          title = paste("Files for", year)
        ) %>%
        cols_label(
          Filename = "Filename",
          Type = "Document Type",
          Language = "Language", 
          Extension = "Extension",
          Path = "Full Path"
        ) %>%
        tab_style(
          style = cell_text(size = "small"),
          locations = cells_body(columns = Path)
        )
    } else {
      # Return empty GT table with message
      data.frame(Message = paste("No files found for", year)) %>%
        gt() %>%
        tab_header(title = paste("Files for", year))
    }
  } else {
    # Return message for missing year
    data.frame(Message = paste("Year", year, "not found in data")) %>%
      gt() %>%
      tab_header(title = paste("Files for", year))
  }
}
```

### Year 2022

```{r year-2022-table}
create_year_table("2022")
```

### Year 2023

```{r year-2023-table}
create_year_table("2023")
```

# Download Planning

## Priority Downloads for RAG System

Based on the file inventory, the following files are recommended for initial RAG system ingestion:

```{r download-recommendations}
# Identify key files for RAG system
rag_priority <- filter_files(categorized_files, 
                            file_types = c("data_dictionary", "questionnaire", "user_guide"),
                            languages = "english")

if (length(rag_priority) > 0) {
  rag_df <- data.frame(
    Priority = "High",
    Year = sapply(rag_priority, function(x) x$survey_year),
    Type = sapply(rag_priority, function(x) x$file_type),
    Filename = sapply(rag_priority, function(x) x$filename),
    stringsAsFactors = FALSE
  ) %>%
    arrange(Year, Type)
  
  rag_df %>%
    gt() %>%
    tab_header(
      title = "Recommended Files for RAG System"
    ) %>%
    cols_label(
      Priority = "Priority",
      Year = "Year", 
      Type = "Document Type",
      Filename = "Filename"
    ) %>%
    tab_style(
      style = cell_fill(color = "gold", alpha = 0.3),
      locations = cells_body(
        columns = Priority,
        rows = Priority == "High"
      )
    )
  
  cat("\n**Download Commands:**\n\n")
  cat("```r\n")
  cat("# Download all data dictionaries\n")
  cat("download_data_dictionaries()\n\n")
  cat("# Download all questionnaires\n") 
  cat("download_questionnaires()\n\n")
  cat("# Download user guides\n")
  cat("download_files_by_criteria(file_types = 'user_guide', languages = 'english')\n")
  cat("```\n")
}
```

## Coverage Gaps

```{r coverage-gaps}
# Identify years with missing documentation
all_expected <- get_expected_years()
years_with_files <- as.numeric(names(categorized_files))
missing_years <- setdiff(all_expected, years_with_files)

if (length(missing_years) > 0) {
  cat("**Years with missing documentation:**", paste(missing_years, collapse = ", "), "\n\n")
  cat("These years have folder structures created but no files uploaded yet.\n\n")
} else {
  cat("✓ All expected years have documentation files.\n\n")
}

# Identify document types that are inconsistently available
cat("**Document Type Coverage:**\n\n")
for (type in key_types) {
  type_years <- c()
  for (year in names(categorized_files)) {
    year_types <- sapply(categorized_files[[year]], function(x) x$file_type)
    if (type %in% year_types) {
      type_years <- c(type_years, year)
    }
  }
  
  coverage_pct <- round(length(type_years) / length(names(categorized_files)) * 100, 1)
  cat("- **", gsub("_", " ", stringr::str_to_title(type)), "**: ", 
      length(type_years), " of ", length(names(categorized_files)), 
      " years (", coverage_pct, "%)\n", sep = "")
}
```

# Technical Details

## OSF Project Information

- **Project ID**: `r cchs_structure_data$metadata$osf_project_id`
- **Documentation Component**: `r cchs_structure_data$metadata$osf_documentation_component_id`
- **Last Updated**: `r cchs_structure_data$metadata$files_last_scanned`

## Folder Structure

The standardized CCHS folder structure follows this pattern:

```
YEAR/
├── [CYCLE.1 | 12-Month]/
    └── Master/
        ├── Docs/          # PDF documentation
        └── Layout/        # SAS/SPSS syntax files
```

## Update Instructions

To regenerate this catalog with updated data:

```r
# Update file inventory from OSF
source("R/enhance_structure_with_files.R")
enhanced_data <- enhance_structure_with_files()

# Regenerate catalog
quarto::quarto_render("cchs_catalog.qmd")
```

---

*This catalog was generated automatically from OSF.io data on `r Sys.Date()`.*