---
title: "Statistics Canada CCHS Variable Browser"
subtitle: "Search 14,005 variables across 231 datasets"
author: "cchsflow-docs"
date: last-modified
format:
  html:
    toc: true
    toc-depth: 2
    theme: cosmo
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(DT)
library(dplyr)
library(htmltools)
```

## About this browser

This interactive table contains all **14,005 CCHS variables** from the [Canadian Community Health Survey](https://www.statcan.gc.ca/en/survey/household/3226). Use the search box and column filters to find variables of interest.

**Data source**: Statistics Canada CCHS (metadata via ICES Data Dictionary)
**Version**: 1.2.0

::: {.callout-note}
## Attribution
The Canadian Community Health Survey (CCHS) is conducted by [Statistics Canada](https://www.statcan.gc.ca/). Variable metadata was scraped from the ICES Data Dictionary, which hosts this information for Ontario-based researchers.
:::

::: {.callout-tip}
## Quick tips
- Use **dropdown filters** (below headers) for Regions, File Types, and Ontario Share
- Use **numeric sliders** for Min Year and Max Year
- **Example**: To find Ontario Share files 2001-2015, select "Ontario" from Regions dropdown, select Ontario Share = "Yes", and slide Max Year to ≤ 2015
- Use the **global search box** (top right) to search variable names and labels
- Click **Copy** or **CSV** to export filtered results
:::

## Variables

```{r load-data}
# Load the variables data with enriched metadata
variables <- read.csv("../data/exports/ices_cchs_variables_for_sheets.csv",
                      stringsAsFactors = FALSE)

# Create display-ready table with filtering columns
# Convert categorical columns to factors for dropdown filters in DT
variables_display <- variables |>
  mutate(
    # Create hyperlink to ICES variable page
    Variable = sprintf(
      '<a href="https://datadictionary.ices.on.ca/Applications/DataDictionary/Variables.aspx?Library=CCHS&Name=%s" target="_blank">%s</a>',
      variable_name, variable_name
    ),
    # Clean up display values
    Module = module,
    Label = label,
    Type = type,
    Format = ifelse(is.na(format) | format == "", "-", format),
    Years = year_range,
    `Min Year` = min_year,
    `Max Year` = max_year,
    # Factor columns get dropdown filters instead of text boxes
    Regions = factor(regions),
    `File Types` = factor(file_types),
    `Ontario Share` = factor(ifelse(has_ontario & has_share, "Yes", "No"),
                             levels = c("Yes", "No")),
    Datasets = n_datasets,
    `Sample` = ifelse(
      nchar(sample_datasets) > 50,
      paste0(substr(sample_datasets, 1, 47), "..."),
      sample_datasets
    )
  ) |>
  select(Variable, Module, Label, Years, `Min Year`, `Max Year`,
         Regions, `File Types`, `Ontario Share`, Datasets, `Sample`)
```

```{r variables-table}
datatable(
  variables_display,
  filter = 'top',
  rownames = FALSE,
  escape = FALSE,  # Allow HTML links in Variable column
  extensions = 'Buttons',
  options = list(
    pageLength = 25,
    scrollX = TRUE,
    deferRender = TRUE,
    searchHighlight = TRUE,
    dom = 'Bfrtip',
    buttons = list(
      'copy',
      list(
        extend = 'csv',
        filename = 'cchs_variables_filtered'
      )
    ),
    columnDefs = list(
      list(width = '90px', targets = 0),   # Variable
      list(width = '60px', targets = 1),   # Module
      list(width = '250px', targets = 2),  # Label
      list(width = '70px', targets = 3),   # Years
      list(width = '50px', targets = 4),   # Min Year
      list(width = '50px', targets = 5),   # Max Year
      list(width = '90px', targets = 6),   # Regions
      list(width = '100px', targets = 7),  # File Types
      list(width = '60px', targets = 8),   # Ontario Share
      list(width = '50px', targets = 9),   # Datasets
      list(width = '150px', targets = 10)  # Sample
    ),
    language = list(
      search = "Search all columns:",
      info = "Showing _START_ to _END_ of _TOTAL_ variables"
    )
  ),
  caption = htmltools::tags$caption(
    style = 'caption-side: top; text-align: left; font-size: 1.1em; font-weight: bold;',
    'Click variable name for detailed metadata. Use column filters to narrow by year, region, or file type.'
  )
)
```

## Datasets

```{r load-datasets}
datasets <- read.csv("../data/exports/ices_cchs_datasets_for_sheets.csv",
                     stringsAsFactors = FALSE)

# Prepare display columns with factors for dropdown filters
datasets_display <- datasets |>
  mutate(
    `Dataset ID` = dataset_id,
    Variables = variable_count,
    Year = year_label,
    # Factor columns get dropdown filters
    Region = factor(region),
    Type = factor(dataset_type),
    Cycle = factor(ifelse(is.na(cycle_label) | cycle_label == "Unknown", "-", cycle_label)),
    Supplement = ifelse(is_supplement, supplement_type, "-"),
    Bootstrap = factor(ifelse(is_bootstrap, "Yes", "No"), levels = c("No", "Yes"))
  ) |>
  select(`Dataset ID`, Variables, Year, Region, Type, Cycle, Supplement, Bootstrap) |>
  arrange(desc(Variables))
```

The CCHS collection contains **`r nrow(datasets_display)` datasets**. Datasets vary in size from `r min(datasets_display$Variables)` to `r max(datasets_display$Variables)` variables.

::: {.callout-tip}
## Finding Ontario Share files
Filter the table below by:

- **Region** = "Ontario"
- **Type** = "Share"
- **Bootstrap** = "No" (to exclude bootstrap weight files)

This will show the main Ontario Share datasets used for most analyses.
:::

```{r datasets-table}
datatable(
  datasets_display,
  filter = 'top',
  rownames = FALSE,
  options = list(
    pageLength = 20,
    scrollX = TRUE,
    dom = 'Bfrtip',
    buttons = c('copy', 'csv'),
    order = list(list(1, 'desc')),  # Sort by variable count descending
    columnDefs = list(
      list(width = '180px', targets = 0),  # Dataset ID
      list(width = '70px', targets = 1),   # Variables
      list(width = '80px', targets = 2),   # Year
      list(width = '100px', targets = 3),  # Region
      list(width = '80px', targets = 4),   # Type
      list(width = '120px', targets = 5),  # Cycle
      list(width = '120px', targets = 6),  # Supplement
      list(width = '60px', targets = 7)    # Bootstrap
    ),
    language = list(
      info = "Showing _START_ to _END_ of _TOTAL_ datasets"
    )
  ),
  caption = htmltools::tags$caption(
    style = 'caption-side: top; text-align: left;',
    'Use filters to find specific datasets by year, region, and file type'
  )
)
```

## Data dictionary schema

The underlying data is stored in a DuckDB database with the following structure:

| Table | Rows | Description |
|-------|------|-------------|
| `variables` | 14,005 | Variable metadata (name, label, type, format) |
| `datasets` | 231 | Dataset identifiers and variable counts |
| `variable_availability` | 118,668 | Many-to-many mapping of variables to datasets |
| `value_formats` | 11,065 | Code/label pairs for categorical variables |

## Source and updates

- **Survey**: [Statistics Canada CCHS](https://www.statcan.gc.ca/en/survey/household/3226)
- **Metadata source**: ICES Data Dictionary (scraped January 2026)
- **Repository**: [Big-Life-Lab/cchsflow-docs](https://github.com/Big-Life-Lab/cchsflow-docs)
- **Release**: [ices-cchs-dictionary-v1.0.0](https://github.com/Big-Life-Lab/cchsflow-docs/releases/tag/ices-cchs-dictionary-v1.0.0)

::: {.callout-note}
## Data ownership
The CCHS is owned and maintained by Statistics Canada. This browser provides searchable access to variable metadata only. For survey data access, contact Statistics Canada or your local Research Data Centre.
:::

To update this browser with new data:
1. Re-run the scraper: `Rscript scripts/run_ices_full_scrape_duckdb.R`
2. Regenerate exports: Update `data/exports/` CSVs
3. Re-render this report: `quarto render reports/ices-dictionary-browser.qmd`
